Convective heat transport in stratified atmospheres at low and high Mach number

### 2017-02-22 tex/nusselt_paper.tex
slots new figures into the paper, does not change any of the text

\begin{figure}[t]
\includegraphics[width=3.4375in]{./figs/ma_v_eps.png}
\caption{The maximum value of Ma which has been horizontally 
averaged and time averaged for $\geq 100 t_b$, 
beginning roughly $50t_b$ after
the start of simulations.  This time average is long 
enough that the profile is well converged
and error bars are negligible. (a) For $\epsilon \leq 0.1$,
a scaling of $\text{Ma }\propto \{\epsilon^{0.50}, \epsilon^{0.51}\}$ 
at $\text{Ra }= \{10^2, 10^5\}$ exists.
When $\epsilon \rightarrow m_{\text{ad}}$, 
large deviations from this power law are seen.  
(b) At high $\epsilon$, Ma scales as Ra$^{0.28}$ 
until it reaches the supersonic regime, at which point it
follows a power law of Ra$^{-0.10}$.  At low $\epsilon$, 
consistent power laws are achieved throughout all
values of Ra studied, where 
$\text{Ma }\propto \{\text{Ra}^{0.26},\,\text{Ra}^{0.22}\}$
for $\epsilon = \{10^{-4}, 10^{-7}\}$. 
\label{fig:ma_v_eps} }
\end{figure}

@@

\begin{figure}[t]
\includegraphics[width=3.4375in]{./figs/fluxes_fig.png}
\caption{Time-averaged vertical flux profiles ($F_{\text{z}}$)
for (a) high and (b) low Ma flows at $\text{Ra }= 10^6$.  
All fluxes are defined as in (\ref{eqn:energy_eqn_full}) and 
normalized by $F_{\text{ref}} - F_{\text{A}}$, as in (\ref{eqn:nusselt}).
The dashed lines correspond to the
enthalpy flux (orange, positive) and kinetic energy flux (purple, negative).  
The grey dash-dot line is the
viscous flux and the green dotted line is the conductive flux with the 
adiabatic contribution removed. The potential energy flux is negligible and is not shown.
In (a), the viscous flux is negligible and is not shown.  The solid black line is
Nu, the properly normalized sum of all the fluxes \label{fig:flux_profiles} }
\end{figure}

@@

\begin{figure}[t]
\includegraphics[width=3.4375in]{./figs/nu_v_ra.png}
\caption{Variation of Nu as Ra increases at high and low $\epsilon$. 
At high $\epsilon$ (purple circles), 
a clear transition from the subsonic to supersonic regime is evident in the scaling
of Nu with Ra at $\text{Ra} \approx 10^4$.  In the low $\epsilon$ regime (green diamonds and yellow squares), 
our observed Nu scalings collapse onto a similar line which is
indistinguishable from a $\text{Ra}^{2/7}$ scaling, 
as observed in RB convection \cite{johnston&doering2009}.  Error bars are determined
 by the square root of the variance of the time-averaged Nu profile with depth and 
 indicate whether or not a solution is well-converged.
\label{fig:nu_v_ra} }
\end{figure}

>>>>

\begin{figure}[t]
\includegraphics[width=3.4375in]{./figs/ma_v_Ra.png}
\caption{The maximum value of Ma which has been horizontally 
averaged and time averaged for $\geq 100 t_b$, 
beginning roughly $50t_b$ after
the start of simulations.  This time average is long 
enough that the profile is well converged
and error bars are negligible. (a) For $\epsilon \leq 0.1$,
a scaling of $\text{Ma }\propto \{\epsilon^{0.50}, \epsilon^{0.51}\}$ 
at $\text{Ra }= \{10^2, 10^5\}$ exists.
When $\epsilon \rightarrow m_{\text{ad}}$, 
large deviations from this power law are seen.  
(b) At high $\epsilon$, Ma scales as Ra$^{0.28}$ 
until it reaches the supersonic regime, at which point it
follows a power law of Ra$^{-0.10}$.  At low $\epsilon$, 
consistent power laws are achieved throughout all
values of Ra studied, where 
$\text{Ma }\propto \{\text{Ra}^{0.26},\,\text{Ra}^{0.22}\}$
for $\epsilon = \{10^{-4}, 10^{-7}\}$. 
\label{fig:ma_v_eps} }
\end{figure}

@@

\begin{figure}[t]
\includegraphics[width=3.4375in]{./figs/re_and_nu_v_Ra.png}
\caption{Time-averaged vertical flux profiles ($F_{\text{z}}$)
for (a) high and (b) low Ma flows at $\text{Ra }= 10^6$.  
All fluxes are defined as in (\ref{eqn:energy_eqn_full}) and 
normalized by $F_{\text{ref}} - F_{\text{A}}$, as in (\ref{eqn:nusselt}).
The dashed lines correspond to the
enthalpy flux (orange, positive) and kinetic energy flux (purple, negative).  
The grey dash-dot line is the
viscous flux and the green dotted line is the conductive flux with the 
adiabatic contribution removed. The potential energy flux is negligible and is not shown.
In (a), the viscous flux is negligible and is not shown.  The solid black line is
Nu, the properly normalized sum of all the fluxes \label{fig:re_and_nu_v_Ra} }
\end{figure}

@@

\begin{figure}[t]
\includegraphics[width=3.4375in]{./figs/density_v_ra.png}
\caption{Variation of Nu as Ra increases at high and low $\epsilon$. 
At high $\epsilon$ (purple circles), 
a clear transition from the subsonic to supersonic regime is evident in the scaling
of Nu with Ra at $\text{Ra} \approx 10^4$.  In the low $\epsilon$ regime (green diamonds and yellow squares), 
our observed Nu scalings collapse onto a similar line which is
indistinguishable from a $\text{Ra}^{2/7}$ scaling, 
as observed in RB convection \cite{johnston&doering2009}.  Error bars are determined
 by the square root of the variance of the time-averaged Nu profile with depth and 
 indicate whether or not a solution is well-converged.
\label{fig:nrho_v_ra} }
\end{figure}
